Review of Assigned Readings

### 2018-01-04 paper/paper.tex

Next we display the time series data on bitcoin price development for the observed time period. The first plot shows the hourly changes of bitcoin prices. The second and third plots are once again first difference transormations of the main variable for the later analysis. In this graph we observe a notably volatile movement and no spesific direction. This contradicts the recent trend of rising bitcoin prices in the months, but that happens because we observe a small period of a week in which bitcoin happened to have a neutral price development.\\

>>>>

Next we display the time series data on bitcoin price development for the observed time period. The first plot shows the hourly changes of bitcoin prices. The second and third plots are once again first difference transormations of the main variable for later analysis. In this graph we observe a notably volatile movement with no spesific direction. This contradicts the general rising trend of bitcoin prices of the past months, but the problem may indeed arise if we happen to select a short period of one week when bitcoin price movement behaves less bullishly as usual, in other words, the lack of articulated trend may be attributed to \textit{selection bias}.\\
